---
title: "Setting the template ADMB"
author: "Juan-Carlos Quiroz"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    #css: ../hakeRead.css
vignette: >
  %\VignetteIndexEntry{Setting the template ADMB}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info 

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css
        
Or some code

```c
GLOBALS_SECTION  
  #include <admodel.h> 
  #include <time.h>
  #include <string.h>
  #undef outadmb
  #define outadmb(object) report << #object "\n" << object << endl;
  ... and so
```

```c
REPORT_SECTION 
  outadmb(vages);
  outadmb(vyears);
  outadmb(PeT);
  outadmb(PeP);
  outadmb(PeE);                                                           
  outadmb(strawl);
  outadmb(spal);
  outadmb(sesp);
  outadmb(ssurv);      
  ... and so
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
